COG-ED Manuscript

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
calculation of hypothesis 2a

# for each participant subjective values (SVs) for 1-, 2-, 3-, and 4-back will be calculated
# an ANOVA with six linear contrasts will be calculated, contrasting the SVs of two n-back levels at a time

>>>>

  # ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time

  # make a temporary copy of the SV data frame

  h2a_data <- data_SV
  h2a_data$level <- as.factor(h2a_data$level)

  contrasts(h2a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                     c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

  hypothesis2a_anova <- summary(aov(h2a_data$sv ~ h2a_data$level))
  hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$sv ~ h2a_data$level))

  remove(h2a_data)
